\documentclass[11pt]{article}
\usepackage{amsmath, amssymb}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{algorithmic}

\begin{document}

\section*{Coreset Subsampling}

Given $N$ training samples with soft labels $Y \in \mathbb{R}^{N \times K}$ and domain assignments $D \in \mathbb{Z}^N$, we select a coreset of size $\lfloor \alpha N \rfloor$ (default $\alpha = 0.25$) using one of two strategies. Subsampling is performed independently per domain, with quota proportional to domain size.

\subsection*{Strategy 1: Entropy-Stratified Sampling}

\begin{enumerate}
\item Compute prediction entropy per sample:
\begin{equation}
H_i = -\sum_{k=1}^{K} y_{ik} \log y_{ik}
\end{equation}
\item Assign each sample to a stratum $(c_i, b_i)$ where $c_i = \arg\max_k\, y_{ik}$ is the dominant cell type and $b_i$ is the entropy quantile bin ($B$ bins, default $B=3$).
\item Allocate quota per stratum proportional to its size; sample uniformly within each stratum.
\end{enumerate}

\subsection*{Strategy 2: Greedy $k$-Center}

\begin{enumerate}
\item Pick a random seed point in label space $\mathbb{R}^K$.
\item Greedily select the point farthest (in $\ell_2$) from all current centers.
\item Repeat until $\lfloor \alpha N \rfloor$ points are selected.
\end{enumerate}

\noindent\textbf{Comparison.} Stratified sampling preserves the joint distribution of cell-type identity and label uncertainty. $k$-Center maximizes coverage in label space, ensuring rare cell-type compositions are represented.

\end{document}
